%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Open Source Contributor} % Job title
    {Github} % Organization
    {Global} % Location
    {Jan. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Short URL - Bit.ly alternative}
        \item {Todo App - Todoist alternative}
        \item {Restsuite - Postman, Insomnia alternative ( Java Swing ) }
        \item {Restsuite v2 - Postman, Insomnia alternative ( Kotlin, Jetbrain Compose ) }
        \item {Geo Smart System - Realtime Tracking System ( Golang, Backend ) }
        \item {Geo Smart Map - Realtime Tracking System ( Angular, Frontend ) }
        \item {Geo Smart App - Realtime Tracking System ( Flutter, Mobile ) }
        \item {JWT Go - JWT Library for Golang }
        \item {Mathics - Numpy alternative for Golang }
        \item {Media - Media server, such as image, video, audio, etc ( Golang ) }
        \item {Factory - Swiss Knife Army Tools for DevOps ( Golang ) }
        \item {Operation X - CI/CD Tools ( NodeJS, Express) }
        \item {Stay - Package Manager for Golang }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  {Developing Personal Consume Technology} % Job title
  {Aditama Labs} % Organization
  {Global} % Location
  {Jan. 2018 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Projects Indonesia Notifications System - Notification System for Projects Indonesia, using Golang by Scraping Data }
      \item {Bank Central Asia - BCA API Wrapper for Golang }
      \item {Social Police - Telegram Bot for reporting any kind of social crime in indonesia }
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Full Stack Engineer} % Job title
    {PT. Eigen Tri Mathema} % Organization
    {Bandung, Indonesia} % Location
    {Aug. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing Mini ERP for Phillip Works}
        \item {Developing Medium Size ERP for Mahugi Jaya Sejahtera}
        \item {Maintenance Pipamas Tracking System both Applications and Servers}
        \item {Maintenance Phillip Works App and Servers in AWS Cloud}
        \item {Developing Large Size ERP for PT. PMPS}
        \item {Setup Networking for ERP PT. PMPS using Mikrotik}
        \item {Provisioning Kubernetes Cluster for ERP PT. PMPS}
        \item {Setup On Premise Server for ERP PT. PMPS}
        \item {Managing and Setup On Premise Server for ERP Mahugi Jaya Sejahtera}
        \item {Provisioning Kubernetes Cluster for ERP Mahugi Jaya Sejahtera}
        \item {Create DevOps Culture and utilize fully automation of development cycle in PT. Eigen Tri Mathema, using Docker, CoreDNS, Drone CI, Gitea, Kubernetes, ArgoCD, Prometheus, Grafana, ELK Stack, and many more}
        \item {Managing On Premise Server and Network for PT. Eigen Tri Mathema}
        \item {Managing Cloud Infrastucture for PT. Eigen Tri Mathema using Google Cloud Platform}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Engineer} % Job title
    {PT. Xenos Kreasi Teknologi} % Organization
    {Bandung, Indonesia} % Location
    {Apr. 2018 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing Water Galon Application for Managing Drinking Water Business}
        \item {Maintenance Wifi Bandung Juara Application for Government of Bandung}
        \item {Developing Realtime CCTV for Government of Bandung}
        \item {Developing Mobile, Backend and Frontend for IFGF Semarang}
        \item {Developing Mobile, Backend and Frontend for IFGF Global}
        \item {Developing Mobile, Backend and Frontend for IFGF Bandung}
        \item {Maintenance OPD Bandung Apps}
        \item {Developing Zona Menara Bersama for Kominfo}
        \item {Developing Frontend and Mobile Application for PMPS Tracking System}
        \item {Developing Backend, Frontend and Mobile Beton Tracking System}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Wordpress Developer} % Job title
    {CV. Puri Cipta} % Organization
    {Bandung, Indonesia} % Location
    {Dec. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Convert PSD to HTML for PT. Dickson}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Engineer} % Job title
    {CV. Kurvasoft} % Organization
    {Bandung, Indonesia} % Location
    {Feb. 2017 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing Custom CRM for CV. Pumasindo}
        \item {Developing Medical App for Halmahera Hospital}
        \item {Maintenance Custom ERP Carrefour App ( CT. Corp )}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern Software Engineer} % Job title
    {PT. Jamparing Masagi} % Organization
    {Cimahi, Indonesia} % Location
    {Apr. 2016 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing Mini CMS for Internal Company}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}